---
title: "Fancy Title"
header-includes:
  - \usepackage{graphicx}
  - \usepackage{amsmath}
  - \usepackage{float}
  - \usepackage{hyperref}
  - \usepackage{setspace}
  - \usepackage{booktabs}
  - \onehalfspacing
output:
    pdf_document:
        fig_caption: yes
latex_engine: lualatex
geometry: margin = 2.5cm
bibliography: references.bib
nocite: |
  @dplyr, @magrittr, @infuser, @countrycode, @tidyr, @purrr, @formattable, @webshot, @htmltools, @aod, @devtools, @margins, @mfx, @ggplot2, @gridExtra, @matrix
---

```{r setup, eval = TRUE, echo = FALSE, include = TRUE}
###########################
# IMPORTANT NOTE:
# In order to create the final report, clone the repository from github:
# https://github.com/jgmill/dolores
# and then change the working directory below to where you cloned the repo.

wd = paste0(Sys.getenv("HOME"), "/Documents/dolores/seminar_paper")
knitr::opts_knit$set(root.dir = wd)

```

```{r global_options, include=FALSE, echo=TRUE}
knitr::opts_chunk$set(fig.pos = 'H')
# options(xtable.comment = FALSE,
#         xtable.table.placement="H")
```


\pagenumbering{gobble}

\makeatletter
\renewcommand\paragraph{\@startsection{paragraph}{4}{\z@}%
            {-2.5ex\@plus -1ex \@minus -.25ex}%
            {1.25ex \@plus .25ex}%
            {\normalfont\normalsize\bfseries}}
\makeatother
\setcounter{secnumdepth}{4}
\setcounter{tocdepth}{4}

\bigskip

\begin{center}


Humboldt-Universität zu Berlin \linebreak
School of Business and Economics  \linebreak
Management Science / Heinz-Nixdorf Chair    \linebreak
\medskip


\includegraphics[width=0.2\textwidth]{HU_Logo_small.png}


\textbf{Energy Informatics Computer Based Processing of Energy Data} \linebreak
Summer 2018

\medskip


Seminar Paper by  \linebreak

\textbf{Claudia Günther, Jonathan , Andrew }  \linebreak
576419, ,  \linebreak

\medskip

\medskip


Berlin, 2018-09-15 \linebreak

\end{center}

\medskip

\medskip

\newpage

\listoftables

\newpage

\listoffigures

\newpage

\pagenumbering{arabic}

\tableofcontents

\newpage

\section{Introduction}


\section{Literature Review}


## Headline


\section{Spatiotemporal smoothing of variable renewables}
\subsection{s}

\section{Analysis}
\subsection{Model}
Example code

```{r, eval = FALSE}
[105]  # Labor supply choice tables
[106]  df.female = df.out %>% filter(gender == "FEMALE")
[107]  vars      = names(df.out)[grep("labor", names(df.out))][3:1] # invert
[108]
[109]  labor.supply.f    = lapply(vars, function(x) group.share(df.female, x, 1))
[110]  labor.supply.f.df = do.call(cbind.data.frame, labor.supply.f) %>%
[111]      set_colnames(c("Nonparticipation", "Half time", "Full time"))
```

Example formula

$$ P(Y = 1 | X = x) = \Phi (x' \beta) \tag{1} $$


\subsection{Data}
Example image

```{r fig.cap = " Hello! I am the figure caption. \\label{figurelabel}", fig.height=4, fig.width=4}
library(png)
img = readPNG("images/ger.png")
plot.new() 
rasterImage(img,0,0,1,1)
```

\section{Results}
\subsection{Storage capacity under optimal spatiotemporal smoothing}
\subsection{Sensitivities}


\newpage

\section{Conclusion}

\newpage




\newpage

\section{References}


<div id="refs"></div>


\newpage

\section{Appendix}


\newpage

\begin{Large}
\textbf{Declaration of Authorship}
\end{Large}

\bigskip
\bigskip

We hereby confirm that we have authored this Seminar paper independently and without use
of others than the indicated sources. All passages which are literally or in general matter taken
out of publications or other sources are marked as such.
\bigskip

Berlin, 2018-09-15

\smallskip

\bigskip
